# Cumulative count of set union

Create [cumulative_sets_bars.md](cumulative_sets_bars.md): `R -e 'library(knitr); knit("cumulative_sets_bars.Rmd")'`

Required libraries:
```{r message=FALSE}
library(tidyverse)
```

## Basic case

Create data frame with two columns for set IDs and elements:

```{r}
element <- c("A","B","C","A","A","D","E","F")
id <- c("Set1", "Set1", "Set1", "Set3", "Set2", "Set3","Set3","Set4")
df <- data.frame(id, element)
df
```

Order by set id and increase counter for each additional element to generate a cumulative count of unique elements:

```{r}
df.cc <- df %>% arrange(id) %>% mutate(cc = cumsum(!duplicated(element)))
df.cc
```

Now, collapse the data frame by `id` and assign highest value of `cc` to the new column `ccmax`.
Additionally, add a count for the number of elements in each set and a string with all element names.

```{r}
df.cc.max <- df.cc %>%
  group_by(id) %>%
  summarise(ccmax = max(cc), n_elements=length(element), elements=paste(element,collapse=" "))
df.cc.max
```

Both steps combined into one:
```{r}
library(tidyverse)
df.cc.max <- df %>% arrange(id) %>%
  mutate(cc = cumsum(!duplicated(element))) %>%
  group_by(id) %>%
  summarise(ccmax = max(cc), n_elements=length(element), elements=paste(element,collapse=" "))
```

### Plot

Plot bar chart with set sizes and cumulative sum of set union size (`ccmax`):
```{r cumulative_sets_bars}
ggplot(df.cc.max,aes(x=id,fill=id)) +
  geom_bar(aes(y=n_elements),stat="identity") +
  geom_point(aes(y=ccmax, fill=id),shape=16,size=5) +
  geom_text(y=0.1,aes(label=elements)) +
  theme_bw() + theme(legend.position="none",axis.ticks=element_blank(),panel.grid.minor.y=element_blank()) +
  xlab("") +
  scale_y_continuous("# elements in each set (bars) and cumulative set union (points)",breaks=seq(0,6,1),labels=(seq(0,6,1)))
```

## Subsets
Assign probability to each element:
```{r}
element <- c("A","B","C","A","A","D","E","F")
prob <- c(0.3, 0.8 , 1.0, 0.9, 0.7, 1.0, 0.2, 0.8)
id <- c("Set1", "Set1", "Set1", "Set3", "Set2", "Set3","Set3","Set4")
df <- data.frame(id, prob, element)
df
```
Only count elements with `prob > 0.5`:

```{r}
df.cc <- df %>% arrange(id) %>% filter(prob>0.5) %>% mutate(cc=cumsum(!duplicated(unlist(element))))
df.cc
```

